An Inception Cohort Study Quantifying How Many Registered Studies are Published.

### 2023-05-29 paper.Rmd
incorporating all comments

---
title             : "An Inception Cohort Study Quantifying How Many Registered Studies are Published."
shorttitle        : "QUANTIFYING PUBLISHED REGISTERED STUDIES"
author: 
  - name          : "Eline Ensinck"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author
    email         : "e.n.f.ensinck@student.tue.nl"  
  - name          : "Daniël Lakens"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Den Dolech 1, 5600MB Eindhoven, The Netherlands"
    email         : "D.Lakens@tue.nl"
affiliation:
  - id            : "1"
    institution   : "Eindhoven University of Technology"
authornote: |
  This work was funded by VIDI Grant 452-17-013 from the Netherlands Organisation for Scientific Research. The computationally reproducible version of this manuscript is available at https://github.com/Lakens/registered_published and additional materials on https://osf.io/8uqfb/. 
abstract: |
  We quantified how many research studies registered on the Open Science Framework (OSF) are performed but never publicly shared. Examining 315 registrations revealed that 169 were research studies, of which 104 (62%) were published. For the whole population of registrations on the OSF before November 2017 we estimate 58% is published within at least 4 years. Researchers use registries to make unpublished studies public, and the OSF policy to automatically make registrations public substantially increases the number of performed studies that become known to the scientific community. It is often challenging to identify whether public registrations are published due to a lack of information in registrations. In responses to emails asking researchers why studies remained unpublished, logistics (e.g., lack of time, researchers changing jobs) was the most common reason, followed by null results and rejections during peer review. Our project shows a substantial amount of data that researchers collect is never publicly shared. Selectively publishing studies is problematic because of the possibility that the resources used to collect the data are wasted, and if the publication of studies depend on the results their non-publication can cause bias in the scientific literature. Although it is common knowledge that researchers have studies in their filedrawer, it is extremely difficult to quantify how many studies in psychology are performed, but never published. The OSF has a policy to make all registrations public after four years. This allows us to perform the first inception cohort study on the OSF where we attempt to examine for registered studies if they end up in the scientific literature after at least 4 years. A better understanding of how many studies remain unpublished, and the reasons why researchers did not publish studies, enables researchers to seriously engage with the question how internal inefficiency in science can be reduced.

keywords          : "Publication Bias; File-Drawer; Registry; Research Waste"
wordcount         : "1111"
bibliography      : ["RegistriesPublication.bib"]
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
figsintext        : yes
class             : "jou, a4paper"
output            : papaja::apa6_pdf
link-citations    : true
editor_options: 
  chunk_output_type: console
---

@@

Not all studies scientists perform end up in the scientific literature [@franco_publication_2014; @greenwald_consequences_1975; @sterling_publication_1959]. Studies remain unpublished for a variety of reasons, such as a lack of resources to analyse the results, a loss of interest, perceived methodological weaknesses, or because the results do not support predictions [@easterbrook_publication_1991; @lishner_sorting_2021]. When studies that have the potential to contribute to scientific knowledge go unpublished, research resources are wasted [@buxton_avoiding_2021; @chalmers_avoidable_2009]. The practice of selective publication has been demonstrated in various disciplines, such as psychology, sociology, economics, and medicine [@scheel_excess_2021; @franco_publication_2014; @gerber_publication_2010], but it is challenging to quantify how many studies remain unpublished, and are locked away in the proverbial file drawer [@rosenthal_file_1979].

The most accurate estimates of the percentage of performed studies in the file drawer come from inception cohort studies where studies are – typically retroactively - followed from the moment they are started [@song_dissemination_2010]. Dickersin and colleagues observed that from all 737 studies submitted to two John Hopkins institutional review boards of the school of medicine and the school of health respectively 81% and 66% were published [@dickersin_factors_1992]. Publication bias was mainly caused by researchers not submitting non-significant results, as only 6 out of 124 non-significant results submitted for publication were rejected by a journal. Of 293 clinical trials funded by NIH in 1979 93% was published after a decade [@dickersin_nih_1993]. In the only inception cohort study in the social sciences we know of, Franco et al. [-@franco_publication_2014] found that out of 249 experiments 106 were published in a scientific journal or as a book chapter (45%), 29% of studies were written up but remained unpublished at the time of the study, and 20% (primarily non-significant results) were unpublished and not written up.

One solution to prevent the selective reporting of studies is to require researchers to register their study in a publicly accessible database. An example of such a study registry is ClinicalTrials.gov [@dickersin_evolution_2012]. The requirement to register certain types of studies does not exist in psychology. However, since 2013 the Open Science Framework (OSF) has provided a free study registry for any scientific domain [@spies_open_2013]. The OSF offers researchers the possibility to voluntarily register their study by specifying their hypotheses, methods, and statistical analysis plan.

@@

In this project we aimed to answer four main research questions. First, we were interested in estimating the number of registered studies on the OSF that were performed but remained unpublished after four years. Although this population of studies is not representative of all studies researchers perform (see the discussion), it is more representative of the studies researchers perform than the study by Franco and colleagues [-@franco_publication_2014] as any researcher can register a study on the OSF.

Second, we were interested in whether a registry with the policy to make registration public after an embargo facilitates identifying unpublished studies. By comparing the publication status of registrations manually made public by researchers with registrations automatically opened by the OSF after four years we can estimate how researchers voluntarily share that they have collected data, even when the study remains unpublished, and how often a policy to automatically make a registration public makes performed but unpublished studies findable. This comparison can provide insights into the benefits of a platform that makes registrations public after a certain time, compared to platforms that permanently keep registrations private (e.g., AsPredicted.org).

@@

Finally, while it is useful to quantify how many registered studies remain unpublished after four years, it is equally important to understand why studies remain unpublished. The fourth aim of our study was to contact researchers of registrations of studies that were not publicly shared and ask them whether the study indeed remained unpublished, and if so, ask why their study remains unpublished.

@@

*Data sources*: As registrations become public after four years, we downloaded information about 17.729 registrations created on the OSF before November 18, 2017 (four years before the start of this study) through its application programming interface (API). Registrations are part of at least one associated project page on the OSF. Sometimes researchers still work on projects four years after a registration, and we saw continued activity in some registrations in our sample. The final classification was based on whether the projects were public in April 2022. For `r sum(res_df$project_public == TRUE)` registrations (`r round(100 * sum(res_df$project_public == TRUE)/length(res_df$parent_project), 2)`%) the associated project was public, while for the remaining `r sum(res_df$project_id == "NA")`  registrations (`r round(100 * sum(res_df$project_id == "NA")/length(res_df$parent_project), 2)`%) the associated project is private. We sampled registrations from both these groups. During data analysis we made sure that we did not include the same study twice (even though a single study can have multiple registrations, for example because an analysis subcomponent and a hypothesis subcomponent each get a separate ID in the OSF database). Our sampling strategy means that a study with multiple registrations is more likely to be included in our final sample.

@@

*Classifying Publication Status*: Studies can be available in different degrees, ranging from never being analysed (for example because the researcher who collected the data no longer works in science) to presented at a conference, to being published in a peer reviewed journal [@lishner_sorting_2021]. We considered a study ‘published’ if the study was communicated in any form that allows other researchers to learn about the results. In the remainder of this article the term ‘published’ is used when we classified studies as publicly shared because they appeared in the peer reviewed literature, but also when they were shared as a preprint, a PhD thesis in a stable repository, or a poster or conference paper that described the study in sufficient detail to include it in a meta-analysis (see the online supplementary material for more detail). We did not include bachelor or master theses because even though these can eventually be published (as this article demonstrates) they primarily have an educational goal and we do not consider the file drawer problem equally applicable to this category of studies. This use of the term ‘published’ differs from other inception cohort studies (e.g., Franco et al., 2014) which limit publication to journal articles. We believe the rise of preprints and stable repositories warrants a broader definition of what it means to publish the results of a study, and especially preprints can provide an important outlet for studies that a researcher might decide not to submit to a scientific journal.

@@

*Inclusion criteria*: After some projects were reclassified during the data analysis in total `r sum(included_after$n)` randomly chosen registrations from both groups were examined to see whether they met the selection criteria of our study. Of these, the associated project was public for `r included_after$n[1]` registrations and the associated project was closed for `r included_after$n[2]` registrations. Registrations needed to be actual research studies, as we are interested in estimating how many studies remain unpublished when researchers had the goal to publish. We therefore coded and excluded registrations that were (1) withdrawn, (2) performed for practice purposes (e.g. student assignments or trial registrations), (3) used to generate a stable DOI for supplementary materials at the end of a project, and studies that are much less susceptible to publication bias such as (4) Registered Reports, [@allen_open_2019; @scheel_excess_2021; @chambers_past_2022], and (5) multi-lab projects (i.e., the Reproducibility Project: Psychology).

The number of included and excluded registrations in the sample is summarized in Table \@ref(tab:table-included). We originally included `r sum(included_before$sum_before)` registrations. After excluding `r sum(included_before$sum_before) - sum(included_after$sum_after)` registrations based on email responses for being student projects, performed without the goal of publishing the data, or part of a multi-lab project, our final sample size consists of `r sum(included_after$sum_after)` registrations, where for `r included_after$sum_after[1]` registrations the main project was public and for `r included_after$sum_after[2]` registrations the main project was not public.  An overview of how often registrations were excluded for each of the 5 inclusion criteria is provided in Table \@ref(tab:table-excluded).

@@

*Identifying Publications Corresponding to Registrations*: We attempted to find a publication (e.g., a journal article, preprint, thesis, or scientific poster) associated with each registration included in the analysis. Ideally, it is possible to find a publication associated with a registration without the help of the researchers who performed the study. In practice, due to the often limited information included in a registration on the OSF, information provided by the researchers improved our ability to classify registrations as publicly shared or not. If a publication could be found that provided a direct link to the OSF registration we could be certain that we found the publication corresponding to the registration. In many cases, especially when registrations on the OSF contained little information, and publications did not link to a registration on the OSF, there was some uncertainty about whether a paper corresponded to a registration. Furthermore, if no publication could be found, there always remained the possibility that we failed to find it. Based on an extensive search (for details, see the online supplement) we classified `r table(registration_data_included$published_before_email)[2]` out of the `r sum(included_after$sum_after)` registrations as published, `r table(registration_data_included$published_before_email)[3]` registrations as unpublished, and for `r table(registration_data_included$published_before_email)[4]` registrations we were uncertain about whether the registration was published, for example because we found a paper on the same topic, but this paper did not contain a link to the OSF registration, or there was very little information in the registration.

@@

reasons_table <- registration_data_included %>% group_by(classification) %>% summarise(results = sum(reason_if_unpublished == 1 | reason_if_unpublished == 4 | reason_if_unpublished == 11), review = sum(reason_if_unpublished == 3 | reason_if_unpublished == 14), not_goal_to_publish = sum(reason_if_unpublished == 6 | reason_if_unpublished == 7 | reason_if_unpublished == 9), planning = sum(reason_if_unpublished == 2 | reason_if_unpublished == 5 | reason_if_unpublished == 8 | reason_if_unpublished == 10 | reason_if_unpublished == 13 | reason_if_unpublished == 15 | reason_if_unpublished == 16), study_design = sum(reason_if_unpublished == 12))
reasons_table[3,] <- reasons_table[1,] + reasons_table[2,]
reasons_table <- as.data.frame(reasons_table[,-1])
rownames(reasons_table) <- c("Manually Opened", "Automatically Opened", "Total")
colnames(reasons_table) <- c("Results", "Peer Review", "Not Goal to Publish", "Planning", "Study Design")

@@

There can be many reasons why a researcher does not publish a performed study. We classified the responses given by researchers into 5 categories (see Table \@ref(tab:table-reasons), for a more detailed overview, see the online supplement). Researchers indicated that their motivation to not publish was based on (1) the results of the study, such as null or unclear results and failed replications (`r round(100* reasons_table[3,1]/sum(reasons_table[3,]),0)`%), (2) the review process, such as that the paper was rejected, or that reviewers thought it would be better to leave this study out (`r round(100*reasons_table[3,2]/sum(reasons_table[3,-1]),0)`%), (3) the goal of the study, which was not publishing the results because the project was educational or intended to be shared with stakeholders (`r round(100* reasons_table[3,3]/sum(reasons_table[3,]),0)`%), (4) planning, such as a lack of time, or a new job on a different research topic or outside of academia (`r round(100* reasons_table[3,4]/sum(reasons_table[3,]),0)`%), and (5) problems with the study design (`r round(100* reasons_table[3,5]/sum(reasons_table[3,]),0)`%).

According to the responses we received, issues related to ‘planning’ are the biggest cause of unpublished studies in our sample. Researchers leave academia and fail to complete a project before their contract ends, move on to a new position with a different research focus, or experience a lack of time to complete this specific project given other responsibilities. In some of these cases researchers did intend to come back to this project, and we observed continuing activity in projects registered more than four years ago, including publications that appeared in the literature.

@@

reasons_closed_project_table <- registration_data %>% summarise(results = sum(motivation_not_opening_project == 1), publication_process = sum(motivation_not_opening_project == 2 | motivation_not_opening_project == 10), no_new_information = sum(motivation_not_opening_project == 4 | motivation_not_opening_project == 5 | motivation_not_opening_project == 7 | motivation_not_opening_project == 8 | motivation_not_opening_project == 9 | motivation_not_opening_project == 14), planning = sum(motivation_not_opening_project == 11 | motivation_not_opening_project == 6), technical_issues = sum(motivation_not_opening_project == 12 | motivation_not_opening_project == 13), forgotten = sum(motivation_not_opening_project == 3), other = sum(motivation_not_opening_project == 15 | motivation_not_opening_project == 16))
reasons_closed_project_table <- as.data.frame(reasons_closed_project_table)
rownames(reasons_closed_project_table) <- c("Reasons")
colnames(reasons_closed_project_table) <- c("Results", "Publication Process", "No New Information", "Planning", "Technical Issues", "Forgotten", "Other")
reasons_closed_project_table

@@

Our examination of `r sum(included_after$sum_after)` registrations led to an estimated publication rate of `r round(100*result_population[4], 2)`%, for all registrations on the Open Science framework that were created before November 18, 2017. Extrapolating from our sample, we estimate that of the  `r estimated_nonpublication[3,4]` registered research studies on the OSF that met our inclusion criteria, `r estimated_nonpublication[3,7]` remain unpublished. The main reason researchers give when asked why their studies remain unpublished are logistical issues related to a lack of time, or responsible researchers moving on to a new job. Our study provides an important datapoint to understand how many studies are performed, but never shared. The possibility that around `r 100-round(100*result_population[4], 2)`% of research studies registered on the OSF (excluding multi-lab studies and Registered Reports) are not shared should make scientists reflect on the efficiency of scientific research. Although not all unreported studies necessarily reflect research waste, and science will never be perfectly efficient, our results suggest scientists might need to seriously engage with the question how internal inefficiency can be reduced [@bernal_social_1939; @chalmers_avoidable_2009], wherever this waste is avoidable.

The fact that for `r round(100*reasons_table[3,2]/sum(reasons_table[3,]),0)`% of unpublished studies researchers indicated that the reason that the study remained unpublished is due to the results (e.g., null results or failed replications) is concerning, and considered unacceptable by the general public [@bottesini_what_2022; @pickett_questionable_2017]. It is possible that the  absence of these studies contributes to publication bias in the scientific literature. Researchers can prevent the results of a study from influencing the probability that their study will be published by submitting their registration as a Registered Report [@chambers_past_2022; @nosek_registered_2014]. Compared to the standard literature, where almost all studies support their hypotheses, Registered Reports are much more likely to report null results [@allen_open_2019; @scheel_excess_2021]. If researchers do not report failed replications it is impossible to correct false positive claims in the scientific literature, and if null-results remain unreported effect size estimates in meta-analyses will be inflated to an extent. With the rise of data repositories and preprints it has become feasible and easy to share the results of studies.

It is important to keep in mind that our estimate of the number of registrations on the OSF that are published after four years has 1) remaining uncertainty, and 2) is unlikely to generalize beyond the specific context of our study. First, even after contacting researchers, due to non-response some registrations will be classified incorrectly, and the true number of unpublished studies in our sample could differ slightly from the numbers we report. Second, the estimate is specific to the context of our study, which were all registrations on the Open Science Framework created before November 18, 2017. Users of the OSF in these years are early adopters interested in open science practices. It is possible that this group of researchers differs in how likely they are to share studies they have performed compared to researchers who did not register in this time-window, for example because researchers who adopt open science practices early more actively aim to publish null results, or reduce the size of their file-drawer. We studied the probability that a registered study was published, which might differ from the probability that a non-registered study is published. Registering a study requires work, and it is possible that researchers only register studies they feel have a higher probability of being submitted for publication. Because the practice of registering studies on the OSF up to 2017 was more widespread in experimental social psychology, it remains unknown how many studies remain unpublished in other disciplines. The probability that researchers have the time to share data from a registered study might change over time, and could be higher due to the COVID pandemic. In short, it is unclear whether our estimates generalize to different populations of scientists, different populations of studies, different disciplines, and whether this estimate remains stable over time.

However, our goal was not to establish a generalizable estimate. The variation in the percentage of unpublished studies across scientific contexts is undoubtedly large. At the same time, the factors that cause researchers to not publish results (e.g., a lack of time, responsible researchers leaving academia, null results, rejections during peer review) play a role in many (if not all) scientific contexts. Our study demonstrates that the percentage of unpublished studies can be high, and deserves attention across scientific contexts where similar factors preventing the publication of studies play a role. In fields where most studies are submitted as a Registered Report, researchers work in larger teams where one team member takes over the work of a colleague who leaves academia, and all studies are designed to have a high probability to yield informative results, so there might be few unpublished studies. In fields where Registered Reports are rare, team science is less common, and less informative studies are designed, estimates of published results might be similar to those observed in our sample. Researchers who take efficient knowledge generation in their own scientific context seriously might want to empirically examine the question how many studies go unpublished to determine if there is room for improvement.

*Recommendations for Registries*. We found that registrations are not only used to register a study, but also to create a stable archive after a study has been completed. To be able to distinguish these uses of registries, it might be useful to create separate categories of registrations (e.g., distinguishing ‘prospective registration’ or ‘preregistration’ from ‘post registration’ or ‘data archiving’). A third registration option should be created for all registrations that are done for purely educational or practice purposes. The content of these registrations could remain the same, but some features (such as the automatically created DOI) could be omitted to save money. It would be useful for meta-scientific research if the API that allows researchers to access data from the registry could distinguish different types of registrations (e.g., pre- and post-registrations), and if the API made it possible to retrieve whether a registration was made public manually, or automatically after 4 years.  Lastly, the OSF currently displays registrations of separate components of the same project as unique registrations. It would be clearer if separate components belonging to the same registration would not be displayed as the same registrations. Alternatively, an extra field could be added that indicates that a registration is a sub-component of a certain larger project.

>>>>

---
title             : "An Inception Cohort Study Quantifying How Many Registered Studies are Published."
shorttitle        : "QUANTIFYING PUBLISHED REGISTERED STUDIES"
author: 
  - name          : "Eline Ensinck"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author
    email         : "e.n.f.ensinck@student.tue.nl"  
  - name          : "Daniël Lakens"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Den Dolech 1, 5600MB Eindhoven, The Netherlands"
    email         : "D.Lakens@tue.nl"
affiliation:
  - id            : "1"
    institution   : "Eindhoven University of Technology"
authornote: |
  This work was funded by VIDI Grant 452-17-013 from the Netherlands Organisation for Scientific Research. The computationally reproducible version of this manuscript is available at https://github.com/Lakens/registered_published and additional materials on https://osf.io/8uqfb/. We would like the thanks Stephen Lindsay, Cristian Mesquida Caldentey, and Henry Wyneken for feedback on a draft. 
abstract: |
  We quantified how many studies registered on the Open Science Framework (OSF) up to November 2017 are performed but never shared. Examining a sample of 315 registrations, of which 169 were research studies, we found that 104 (62%) were published. We estimate that 5550 out of 9544 (58%) of registrations on the OSF are published within at least 4 years. Researchers use registries to make unpublished studies public, and the OSF policy to automatically make registrations public substantially increases the number of performed studies that become known to the scientific community. In responses to emails asking researchers why studies remained unpublished, logistical issues (e.g., lack of time, researchers changing jobs) was the most common reason, followed by null results and rejections during peer review. Our study shows that a substantial amount of data that researchers collect is never publicly shared.

keywords          : "File Drawer; Registries; Research Waste; Scientific Publication"
wordcount         : "4501"
bibliography      : ["RegistriesPublication.bib"]
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
figsintext        : yes
class             : "jou, a4paper"
output            : papaja::apa6_pdf
link-citations    : true
editor_options: 
  chunk_output_type: console
---

@@

Not all studies that scientists perform end up in the scientific literature [@franco_publication_2014; @greenwald_consequences_1975; @sterling_publication_1959]. Studies remain unpublished for a variety of reasons, such as a lack of resources to analyse the results, a loss of interest, perceived methodological weaknesses, or because the results do not support predictions [@easterbrook_publication_1991; @lishner_sorting_2021]. When studies that have the potential to contribute to scientific knowledge go unpublished research resources are wasted [@buxton_avoiding_2021; @chalmers_avoidable_2009]. Although it is challenging to quantify how many studies remain unpublished the existence of the proverbial file drawer [@rosenthal_file_1979] has been demonstrated in disciplines such as psychology, sociology, economics, and medicine [@scheel_excess_2021; @franco_publication_2014; @gerber_publication_2010; @dickersin_factors_1992].

The most accurate estimates of the percentage of performed studies in the file drawer come from inception cohort studies where studies are – typically retroactively - followed from the moment they are started [@song_dissemination_2010]. For example, Dickersin and colleagues observed that from all studies approved by two institutional review boards serving the school of medicine and the school of health at the John Hopkins University 81% and 66% were published, respectively [@dickersin_factors_1992]. In the only inception cohort study in the social sciences we know of, Franco, Malhotra, and Simonovits [-@franco_publication_2014] found that out of 249 experiments 106 were published in a scientific journal or as a book chapter (45%), 29% of studies were written up but remained unpublished at the time of the study, and 20% (primarily non-significant results) were unpublished and not written up.

One way to make all studies that have been performed known to peers is to require researchers to (pre)register their study in a publicly accessible database [@dickersin_evolution_2012]. Registries often require researchers to update a registered study with the results. An example of such a study registry is ClinicalTrials.gov. The requirement to register certain types of studies does not exist in psychology. However, since 2013 the Open Science Framework (OSF) has provided a free study registry for any scientific domain [@spies_open_2013]. The OSF offers researchers the possibility to voluntarily register their study by specifying their hypotheses, methods, and statistical analysis plan.

@@

In this project we aimed to answer four main research questions. First, we were interested in estimating the number of registered studies on the OSF that were performed but remained unpublished after four years. Although registered studies are only a subset of all studies researchers perform, in the results section we estimate that our findings apply to 9,544 research studies registered on the OSF up to November 2017.

Second, we were interested in whether a registry with the policy to make registration public after an embargo facilitates identifying unpublished studies. By comparing the publication status of registrations manually made public by researchers with registrations automatically opened by the OSF after four years we can answer two questions. How often do researchers voluntarily share information about their study, even when the study remains unpublished? And how often do we learn about performed but unpublished studies because of the OSF policy to automatically make registrations public after four years?  Answers to these questions can provide insights into the benefits of a platform that makes registrations public after a certain time (e.g., OSF), compared to platforms that permanently keep registrations private (e.g., AsPredicted.org).

@@

Finally, while it is useful to quantify how many registered studies remain unpublished after four years, it is equally important to understand why studies remain unpublished. The fourth aim of our study was to contact researchers of registrations of studies that were not published and ask why their study remains unpublished.

@@

*Data sources*: As registrations become public after four years, we downloaded all information that can be retrieved through the application programming interface (API) of the OSF for 17.729 registrations that were created before November 18, 2017 (four years before the start of this study). Registrations are part of at least one associated project page on the OSF. Sometimes researchers still work on projects four years after a registration, and we saw continued activity in some registrations in our sample. The final classification was based on whether the projects were public in April 2022. For `r sum(res_df$project_public == TRUE)` registrations (`r round(100 * sum(res_df$project_public == TRUE)/length(res_df$parent_project), 2)`%) the associated project was public, while for the remaining `r sum(res_df$project_id == "NA")`  registrations (`r round(100 * sum(res_df$project_id == "NA")/length(res_df$parent_project), 2)`%) the associated project was private. We randomly sampled registrations from both these groups. During data analysis we made sure that we did not include the same study twice (even though a single study can have multiple registrations, for example because an analysis subcomponent and a hypothesis subcomponent each get a separate ID in the OSF database). Our sampling strategy increased the probability that studies with multiple registrations were included in the study.

@@

*Classifying Publication Status*: Studies can be available in different degrees, ranging from never being analysed (for example because the researcher who collected the data no longer works in science) to presented at a conference, to being published in a peer reviewed journal [@lishner_sorting_2021]. We considered a study ‘published’ if the study was communicated in any form that allows other researchers to learn about the results. In the remainder of this article the term ‘published’ is used when we classified studies as publicly shared because they appeared in the peer reviewed literature, but also when they were shared as a preprint, a PhD thesis in a stable repository, or a poster or conference paper that described the study in sufficient detail to include it in a meta-analysis (see the online supplementary material for more detail). We did not include bachelor or master theses because even though these can eventually be published (as this article demonstrates) they primarily have an educational goal and we do not consider the file drawer problem equally applicable to this category of studies. Our definition of ‘published’ is broader than in previous inception cohort studies (e.g., @dickersin_factors_1992; @franco_publication_2014). We believe the rise of preprints and stable repositories warrants a broader definition of what it means to publish the results of a study, especially because preprints provide a possible outlet for studies that a researcher might decide not to submit to a scientific journal.

@@

*Inclusion criteria*: In total `r sum(included_after$n)` randomly chosen registrations from manually and automatically opened registrations were examined to see whether they met the selection criteria of our study. Of these, the associated project was public for `r included_after$n[1]` registrations and the associated project was closed for `r included_after$n[2]` registrations. Registrations needed to be actual research studies, as we are interested in estimating how many studies remain unpublished when researchers had the goal to publish. We therefore coded and excluded registrations that were (1) withdrawn (e.g., all content is removed because an error was made in the registration, but the meta-data continues to exist), (2) performed for practice purposes (e.g. student assignments or trial registrations), (3) used to generate a stable DOI for supplementary materials at the end of a project, and studies that are unlikely to end up in the file drawer such as (4) Registered Reports, [@allen_open_2019; @scheel_excess_2021; @chambers_past_2022], and (5) multi-lab projects (i.e., the Reproducibility Project: Psychology).

The number of included and excluded registrations in the sample is summarized in Table \@ref(tab:table-included). We originally included `r sum(included_before$sum_before)` registrations. After excluding `r sum(included_before$sum_before) - sum(included_after$sum_after)` registrations based on email responses for being student projects, performed without the goal of publishing the data, or part of a multi-lab project, our final sample size consists of `r sum(included_after$sum_after)` registrations. Of these, `r included_after$sum_after[1]` registrations were categorized as manually opened and `r included_after$sum_after[2]` registrations were categorized as automatically opened.  An overview of how often registrations were excluded for each of the 5 inclusion criteria is provided in Table \@ref(tab:table-excluded).

@@

*Identifying Publications Corresponding to Registrations*: We attempted to find a publication (e.g., a journal article, preprint, thesis, or scientific poster) associated with each registration included in the analysis. Ideally, it is possible to find a publication associated with a registration without the help of the researchers who performed the study. In practice, due to the often limited information included in a registration on the OSF, information provided by the researchers improved our ability to classify registrations as publicly shared or not. If a publication could be found that provided a direct link to the OSF registration we could be certain that we found the publication corresponding to the registration. In many cases, especially when registrations on the OSF contained little information, and publications did not link to a registration on the OSF, there was some uncertainty about whether a paper corresponded to a registration. Furthermore, if no publication could be found, there always remained the possibility that we failed to find it. Based on an extensive search (for details, see the online supplement) we classified `r table(registration_data_included$published_before_email)[2]` out of the `r sum(included_after$sum_after)` registrations as published, `r table(registration_data_included$published_before_email)[3]` registrations as unpublished, and for `r table(registration_data_included$published_before_email)[4]` registrations we were uncertain about whether the registration was published. We remained uncertain when, for example, there was very little information in the preregistration, and the information that was available seemed related to a paper without a link to an OSF registration.

@@

reasons_table <- registration_data_included %>% group_by(classification) %>% summarise(planning = sum(reason_if_unpublished == 2 | reason_if_unpublished == 5 | reason_if_unpublished == 8 | reason_if_unpublished == 10 | reason_if_unpublished == 13 | reason_if_unpublished == 15 | reason_if_unpublished == 16), results = sum(reason_if_unpublished == 1 | reason_if_unpublished == 4 | reason_if_unpublished == 11), review = sum(reason_if_unpublished == 3 | reason_if_unpublished == 14), study_design = sum(reason_if_unpublished == 12), not_goal_to_publish = sum(reason_if_unpublished == 6 | reason_if_unpublished == 7 | reason_if_unpublished == 9))
reasons_table[3,] <- reasons_table[1,] + reasons_table[2,]
reasons_table <- as.data.frame(reasons_table[,-1])
rownames(reasons_table) <- c("Manually Opened", "Automatically Opened", "Total")
colnames(reasons_table) <- c("Logistical Issues", "Results", "Peer Review", "Study Design", "Not Goal to Publish")

@@

There can be many reasons why a researcher does not publish a performed study. We classified the responses given by researchers into 5 categories (see Table \@ref(tab:table-reasons), for a more detailed overview, see the online supplement). Researchers indicated that their motivation to not publish was based on (1) logistical issues, such as a lack of time, or a new job on a different research topic or outside of academia (`r round(100*reasons_table[3,1]/sum(reasons_table[3,]),0)`%), (2) the results of the study, such as null or unclear results and failed replications (`r round(100* reasons_table[3,2]/sum(reasons_table[3,]),0)`%), (3) the review process, such as that the paper was rejected, or that reviewers thought it would be better to leave this study out (`r round(100*reasons_table[3,3]/sum(reasons_table[3,]),0)`%), (4) problems with the study design, such as not reaching the intended sample size, or a statistical artifact (`r round(100* reasons_table[3,4]/sum(reasons_table[3,]),0)`%), and (5) the goal of the study, which was not publishing the results because the project was educational or intended to be shared with stakeholders (`r round(100* reasons_table[3,5]/sum(reasons_table[3,]),0)`%).

According to the responses we received, logistical issues are the biggest cause of unpublished studies in our sample. Researchers leave academia and fail to complete a project before their contract ends, move on to a new position with a different research focus, or experience a lack of time to complete this specific project given other responsibilities. In some of these cases researchers did intend to come back to this project, and we observed continuing activity in projects registered more than four years ago, including publications that appeared in the literature.

@@

reasons_closed_project_table <- registration_data %>% summarise(results = sum(motivation_not_opening_project == 1), publication_process = sum(motivation_not_opening_project == 2 | motivation_not_opening_project == 10), no_new_information = sum(motivation_not_opening_project == 4 | motivation_not_opening_project == 5 | motivation_not_opening_project == 7 | motivation_not_opening_project == 8 | motivation_not_opening_project == 9 | motivation_not_opening_project == 14), planning = sum(motivation_not_opening_project == 11 | motivation_not_opening_project == 6), technical_issues = sum(motivation_not_opening_project == 12 | motivation_not_opening_project == 13), forgotten = sum(motivation_not_opening_project == 3), other = sum(motivation_not_opening_project == 15 | motivation_not_opening_project == 16))
reasons_closed_project_table <- as.data.frame(reasons_closed_project_table)
rownames(reasons_closed_project_table) <- c("Reasons")
colnames(reasons_closed_project_table) <- c("Results", "Publication Process", "No New Information", "Logistical Issues", "Technical Issues", "Forgotten", "Other")
reasons_closed_project_table

@@

Our examination of `r sum(included_after$sum_after)` registrations led to an estimated publication rate of `r round(100*result_population[4], 2)`%, for all registrations on the Open Science framework that were created before November 18, 2017. Extrapolating from our sample, we estimate that of the  `r estimated_nonpublication[3,4]` registered research studies on the OSF that met our inclusion criteria, `r estimated_nonpublication[3,7]` remain unpublished. Our study provides an important datapoint to understand how many studies are performed, but never shared. The possibility that around `r 100-round(100*result_population[4], 2)`% of research studies registered on the OSF (excluding multi-lab studies and Registered Reports) are not shared should make scientists reflect on the efficiency of scientific research. Although not all unreported studies necessarily reflect research waste, and science will never be perfectly efficient, our results suggest scientists might need to seriously engage with the question how internal inefficiency can be reduced [@bernal_social_1939; @chalmers_avoidable_2009], wherever this waste is avoidable.

The main reason researchers give when asked why their studies remain unpublished are logistical issues related to a lack of time, or responsible researchers moving on to a new job. Better time-management, designing projects from the outset in a way that they can be completed by other team members, or making unfinished projects available to potential collaborators could mitigate these issues. The fact that for `r round(100*reasons_table[3,2]/sum(reasons_table[3,]),0)`% of unpublished studies researchers indicated that the reason that the study remained unpublished is due to the results (e.g., null results or failed replications) is concerning, and considered unacceptable by the general public [@bottesini_what_2022; @pickett_questionable_2017]. It is possible that the  absence of these studies contributes to publication bias in the scientific literature. Researchers can prevent the results of a study from influencing the probability that their study will be published by submitting their registration as a Registered Report [@chambers_past_2022; @nosek_registered_2014]. If researchers do not report failed replications it is impossible to correct false positive claims in the scientific literature [@schmidt_shall_2009], and if null-results remain unreported effect size estimates in meta-analyses will be inflated [@egger_bias_1997].

Our estimate has remaining uncertainty as some registrations for which authors did not respond to our email might be classified incorrectly. Furthermore, the estimate is specific to the context of our study, which were all registrations on the OSF created before November 18, 2017. Users of the OSF in these years are early adopters interested in open science practices, and the likelihood they share a study might differ from researchers who do not use the OSF. Our estimate might not generalize to non-registered studies. The estimate might also change over time (e.g., more studies might have remained unpublished during the COVID pandemic). In short, the exact percentage of studies that remain unpublished will be different in other contexts.

At the same time, the factors that cause researchers not to publish results (e.g., a lack of time, responsible researchers leaving academia, null results, rejections during peer review) play a role in many (if not all) scientific contexts. In fields where most studies are submitted as a Registered Report, researchers work in larger teams where one team member takes over the work of a colleague who leaves academia, and all studies are designed to have a high probability to yield informative results, there might be less reason to be concerned about the number of unpublished studies. Our study demonstrates that the percentage of unpublished studies can be high. The question how many studies remain unpublished deserves attention across scientific contexts where similar factors preventing the publication of studies play a role.  Empirically examining the size of the file drawer can determine if there is room for improvement.

*Recommendations for Registries*. We found that the OSF is not only used to (pre)register a study, but also to create a stable archive after a study has been completed. To be able to distinguish these uses of registries, it might be useful to create separate categories of registrations (e.g., distinguishing ‘preregistration’ from ‘data archiving’). Allowing users to distinguish educational projects from research projects might also be useful. It would be useful for meta-scientific research if the API that allows researchers to access data from the registry made it possible to retrieve whether a registration was made public manually or automatically by the OSF.  Lastly, the OSF currently displays registrations of separate components of the same project as unique registrations. It would be clearer if one could identify when registrations of components are part of the registration of the overarching project.
